Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-04-18 PAPER/main.tex
minor changes

One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004. A set $\mathcal{I}$ of rectangular items of equal height $h$ made from cardboard are to be packed onto a strip of heigh $h$ from left to right. Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places. A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:boxknife}). However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry). The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$. Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively. Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance. Specifically, as the items are packed from left to right, this involves checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip. The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.

@@

Observe that, in this particular strip-packing problem, the widths of the individual items are disregarded entirely, since the aim is to arrange the items onto a strip of seemingly infinite length. In practical applications, strips of material are often provided in fixed lengths. Given a large problem instance, multiple strips may therefore be required to feasibly accommodate all of the items. For this reason, we define a new problem to be investigated.

\begin{definition}
	\label{defn:scspp}
	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
\end{definition}

>>>>

One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004. A set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of heigh $H$ from left to right. Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places. A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:boxknife}). However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry). The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$. Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively. Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance. Specifically, as the items are packed from left to right, this involves checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip. The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.

@@

Observe that, in this particular strip-packing problem, the widths of the individual items are disregarded entirely, since the aim is to arrange the items onto a strip of seemingly infinite width. In practical applications, strips of material are often provided in fixed widths. Given a large problem instance, multiple strips may therefore be required to feasibly accommodate all of the items. For this reason, we define a new problem to be investigated.

\begin{definition}
	\label{defn:scspp}
	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ of equal fixed width $W$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
\end{definition}
